### 2021-10-06 plos_latex_template.tex
polish rule 8 - Batool

Most importantly, accessibility practices are not afterthoughts that can be dealt with at the last minute. 
They require time and early decision-making \cite{irishIncreasingParticipationUsing2020}. 
Conversely, inaccessible decisions are hard to course-correct, e.g., when finding out too late that a venue is inaccessible for people who use wheelchairs in an in-person conference. 
% Liz: "for people who use whellchairs" rather than "for wheelchairs"

@@

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.
An inclusive communication is to give each individual within the conference a voice and sense of belonging. Embedding inclusion in your communication strategy can only come by design, it should not be a thoughtless default. In the essence of your communication strategy, there should be coherence between actions and words. Always attend to the needs of your team, in other words, don't do anything to the outside that you are not doing for your team.

As you design the promotion plan, actively reach out and promote the conference to people who have been systematically excluded. If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. This could through publishing the diversity statement (e.g., https://user2021.r-project.org/about/diversitystatement/), the code of conduct and accessibility guidelines, and providing fee waivers and financial support.  People who fear getting rejected when applying for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory. If possible, include representative from these communities within the organizing team (rule \ref{rule_diversity}). Also, try to advertise the conference in multiple languages (rule \ref{rule_language}) and express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) to let people know that they are seen, respected, and welcome; that this is their space and community too.

@@

Nevertheless, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community. Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc.

@@

% Rocío: pasting this part of the text here because it may go under Andrea's idea for communication: "Nevertheless, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community. Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc."

@@

%ast: new overall rationale (feel free to comment and change): conferences are expensive to organize and some work on limited budgets. this repercutes in fee costs -but fees for attendance are exclusionary- there should be fees, less no-shows. fees should be set fairly. 
%scholarships or grants to attend are a common way to boost participation from diverse groups but they attract people who believe they'll win -already privileged- people who do not need them but could use the prestige (for lack of another word) to fit in their cv,

>>>>

Most importantly, accessibility practices are not afterthoughts that can be dealt with at the last minute. 
They require time and early decision-making \cite{irishIncreasingParticipationUsing2020}. 
Conversely, inaccessible decisions are hard to course-correct, e.g., when finding out too late that a venue is inaccessible for people who use wheelchairs in an in-person conference.

@@

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.
An inclusive communication is to give each individual within the conference the opportunity to express themselves and a sense of belonging. Embedding inclusion in your communication strategy can only come by design, it should not be a thoughtless default. In the essence of your communication strategy, there should be coherence between actions and words. Always attend to the needs of your team, in other words, don't do anything to the outside that you are not doing for your team.

As you design the promotion plan, actively reach out and promote the conference to people who have been systematically excluded. If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. This could through publishing the diversity statement (e.g., https://user2021.r-project.org/about/diversitystatement/), the code of conduct and accessibility guidelines, and providing fee waivers and financial support. People who fear getting rejected when applying for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory. If possible, include representative from these communities within the organizing team (rule \ref{rule_inclusion}). Also, try to advertise the conference in multiple languages (rule \ref{rule_language}) and express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) to let people know that they are seen, respected, and welcome; that this is their space and community too.

@@

Although conference attendees should have ample opportunities to network with each other, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community(Rule \ref{rule_unbias})). Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc.

@@

@@
